Robust Agglomeration of Labeled Neurons using 3D Skeletonization

### 2017-11-06 papers/cvpr2018/0_introduction.tex
Add one more todo.

\begin{figure}
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
	\caption{We use 3D skeletons to combine neuron labels to full reconstructions.}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
	\caption{We use 3D skeletons to combine neuron labels to full reconstructions. (TODO: Add schematic figure showing the difference between voxel-based / super-voxel based / graph-based algorithms with connections and hierarchy)} %TODO: SCHEMATIC FIGURE
\end{figure}
